### 2019-05-09 peer-review/cover-letter.Rmd
changes for BMJ open

Please find attached our manuscript, entitled “Reassessing the Evidence for Universal School-age Bacillus Calmette Guerin (BCG) Vaccination in England and Wales” for consideration for publication in the journal of Epidemiology and Community Health.

In this paper, we examine a previous analysis of the impact of stopping universal vaccination in England published in the journal of Epidemiology and Community Health in 1989 in light of changing Tuberculosis epidemiology. Using recent surveillance data, together with modern statistical methods to capture uncertainty, we found that the impact of ending the BCG schools’ scheme was greater than previously estimated. Previous estimates were spuriously precise as parameter uncertainty and measurement error were not fully included. Our work highlights the benefits of reproducibility as our study was built on work previously published in this journal.

>>>>

Please find attached our manuscript, entitled “Reassessing the Evidence for Universal School-age Bacillus Calmette Guerin (BCG) Vaccination in England and Wales” for consideration for publication in BMJ Open.

In this paper, we examine a previous analysis of the impact of stopping universal vaccination in England published in the journal of Epidemiology and Community Health in 1989 in light of changing Tuberculosis epidemiology. Using recent surveillance data, together with modern statistical methods to capture uncertainty, we found that the impact of ending the BCG schools’ scheme was greater than previously estimated. Previous estimates were spuriously precise as parameter uncertainty and measurement error were not fully included. Our work highlights the benefits of reproducibility as our study was built on a previously published model.
